Incentivizing Exploration by Heterogeneous Users

### 2018-02-17 introduction.tex
rephrased Theorem 1

Toward that end, we model our setting as follows.
(We describe our model at a high level here,
with formal definitions given in Section~\ref{sec:prob}.)
Arms and users (or \emph{agents}) are characterized by payoff-relevant
\emph{attribute} (or \emph{feature}) vectors.
Arms' attributes are a priori unknown, and
  agents' attributes are drawn from a known distribution.
An agent's reward from pulling an arm is the inner product of his
vector with the arm's vector (plus noise).
When an arm is pulled, a noisy version of its attribute vector is
observed by everyone.
Agents are myopic and will pull the arm whose expected attribute
vector (based on past noisy observations) maximizes their reward.
The principal can incentivize agents to pull particular arms by
offering rewards for the specific arm.
The principal's goal is to keep the cumulative regret across all
agents small, while incurring only small total payments.
Our main theorem can be stated informally as follows:

\begin{theorem} \label{thm:main-intro}
Assume that for each arm, at least a constant fraction of the
population likes this arm best.
If furthermore, the density of ties in agent preferences between arms
vanishes (in a sense made precise in Section~\ref{subsec:discrete}),
there is a policy that achieves constant
expected regret $C$ and constant%
\footnote{The constants $C,C'$ depend on the number of arms and the
  smallest fraction preferring any one arm.} expected payment $C'$.
If near-ties have non-zero density,
then the regret is bounded by $O(C + C'' \log^3(T))$,
while the expected payment is still bounded by $C'$;
here, $C''$ depends on the ``tie density.''
\end{theorem}

>>>>

Toward that end, we model our setting as follows.
(We describe our model at a high level here,
with formal definitions given in Section~\ref{sec:prob}.)
The \ARMNUM arms and users (or \emph{agents})
are characterized by payoff-relevant
\emph{attribute} (or \emph{feature}) vectors.
Arms' attributes are a priori unknown,
and agents' attributes are drawn from a known distribution.
An agent's reward from pulling an arm is the inner product of his
vector with the arm's vector (plus noise).
When an arm is pulled, a noisy version of its attribute vector is
observed by everyone.
Agents are myopic and will pull the arm whose expected attribute
vector (based on past noisy observations) maximizes their reward.
The principal can incentivize agents to pull particular arms by
offering rewards for the specific arm.
The principal's goal is to keep the cumulative regret across all
agents small, while incurring only small total payments.
Our main theorem can be stated informally as follows:

\begin{theorem} \label{thm:main-intro}
Assume that for each arm, at least a constant fraction \MinProb
of the population likes this arm best,
and let \TieDensity be a measure of the ``density of near-ties''
between agents' arms preferences
(in a sense made precise in Section~\ref{subsec:discrete}).
There is a policy that achieves expected 
cumulative regret $O (\ARMNUM \e^{2/\MinProb} + \ARMNUM \log^3(T))$,
using expected cumulative payments of $O(\ARMNUM^2 \e^{2/\MinProb})$.
In particular, when $\TieDensity = 0$
(e.g., in the case of discrete agent preferences),
both the expected regret and expected payment are bounded by constants
(with respect to $T$). 
\end{theorem}
